Fractional Types

### 2019-11-20 fracGC/p.tex
some explanation about extraction

Polymorphic type for ancilla?
\\
First we can inject plain Pi type and value into PiFracDyn:
\INJU{}
and the combinators for Pi can also be inject into PiFracDyn in a straightforward way:
\INJcomb{}
The given injection is correct because it does not change the denotation of type
\INJUeq{}
and the value
\INJVeq{}
Also the interpretation is also consistent:
\INJEvaleq{}
Extract type from PiPointedFrac:
\EXTU{}
Extract combinator:
\EXTUComb{}
The extraction is correct:
\EXTeq{}

>>>>

Polymorphic type for ancilla?
\\
First we can inject plain Pi type and value into PiFracDyn:
\INJU{}
and the combinators for Pi can also be inject into PiFracDyn in a straightforward way:
\INJcomb{}
The given injection is correct because it does not change the denotation of type
\INJUeq{}
,the value
\INJVeq{}
and the interpretation of PiFracDyn is consistent with Pi:
\INJEvaleq{}
To extract a combinator from PiPointedFrac, first we need to extract the corresponding type for PiFracDyn.
Since every type (except Recip) in PiPointedFrac is pointed type so we can always extract a type for plain
Pi and a value from it.
There is no corresponding type of Recip in plain Pi, but we can map it to the
\AgdaOperator{\AgdaInductiveConstructor{𝟙/}}\AgdaSpace{}\AgdaBound{v} type in PiFracDyn.
Note that for all other type the extracted value is erased from type except for
\AgdaOperator{\AgdaInductiveConstructor{𝟙/}}\AgdaSpace{}\AgdaBound{v}
which we still keep it in type.
\EXTU{}
Once we extract the corresponding type we can extract the combinator, the combinators about monad/comonad
just becomes \AgdaInductiveConstructor{id↔} since the information in type is erased:
\EXTUComb{}
And we prove the correctness of the extraction, since the combinators about monad/comonad does not really
computes so for those case the proof is just \AgdaInductiveConstructor{refl},
and for \AgdaInductiveConstructor{∙c} we rely on \AgdaFunction{Eval≡}.
The interesting case is \AgdaInductiveConstructor{ε} where the singleton type guarantee that
the dynamic check is passed.
\EXTeq{}
